### 2022-09-06 draft.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@ffc342bcba49ab4c5e81a9637768acf724056a12 🚀

\hypertarget{data-and-code}{%
\section{Data and code}\label{data-and-code}}

We tested our analytical and heuristic MaxEnt models against open
food-web data queried from three different sources and integrated into
what we call our \emph{complete dataset}. These sources include (1)
terrestrial and aquatic food webs sampled globally and archived on the
ecological interactions database Mangal; (2) freshwater stream food webs
from New Zealand; and (3) aquatic food webs from Tuesday Lake (Michigan,
United States). First, all food webs archived on \texttt{mangal.io}
(Poisot et al. 2016; Banville, Vissault, and Poisot 2021) were directly
queried from the database (\(N = 235\)). Most ecological networks
archived on Mangal are multilayer networks, i.e.~networks that describe
different types of interactions. We kept all networks whose interactions
were mainly of predation and herbivory types, and removed the largest
network (\(S = 714\)) for computational efficiency reasons. Then, to
this set we added food webs from two different sources: the New Zealand
dataset (\(N = 21\); J. P. Pomeranz et al. 2018) and the Tuesday Lake
dataset (\(N = 2\); Cohen, Jonsson, and Carpenter 2003). Our complete
dataset thus contained a total of \(257\) food webs. Of the New Zealand
and Tuesday Lake datasets, \(19\) networks had data on species' relative
abundances that were used in the neutral model (Box 2). These \(19\)
food webs constitute our \emph{abundance dataset}, which is a subset of
our complete dataset.

All code and data to reproduce this article are available at the Open
Science Framework. Data cleaning, simulations and analyses were
conducted in Julia v1.6.1.

@@

@@

We compared the performance of both heuristic MaxEnt models in
predicting these measures to the one of the null
(tbl.~\ref{tbl:measures_all}) and neutral models
(tbl.~\ref{tbl:measures_abund}). Overall, we found that the models based
on the joint degree sequence (i.e.~the type II null and heuristic MaxEnt
models) reproduced the structure of empirical food webs much better than
the ones based on connectance (i.e.~the type I null and heuristic MaxEnt
models). This suggests that the predictive power of connectance might be
more limited than what was previously suggested (Poisot and Gravel
2014). On the other hand, the neutral model of relative abundances was
surprisingly good at predicting the maximum trophic level and the
network diameter. However, with the exception of the network diameter,
the type II heuristic MaxEnt model was better at predicting network
structure than the neutral model for most measures considered. This
might be because, although neutral processes are important, they act in
concert with niche processes in determining species interactions Canard
et al. (2014). The joint degree sequence encodes information on both
neutral and niche processes because the number of prey and predators a
species has is determined by its relative abundance and biological
traits. These results thus show that having information on the number of
prey and predators for each species substantially improves the
prediction of food-web structure, both compared to models solely based
on connectance and to the ones solely based on species relative
abundances.

>>>>

@@

We tested our analytical MaxEnt model against open food-web data queried
from three different sources and integrated into what we call our
\emph{complete dataset}. These sources include (1) terrestrial and
aquatic food webs sampled globally and archived on the ecological
interactions database Mangal; (2) freshwater stream food webs from New
Zealand; and (3) aquatic food webs from Tuesday Lake (Michigan, United
States). First, all food webs archived on \texttt{mangal.io} (Poisot et
al. 2016; Banville, Vissault, and Poisot 2021) were directly queried
from the database (\(N = 235\)). Most ecological networks archived on
Mangal are multilayer networks, i.e.~networks that describe different
types of interactions. We kept all networks whose interactions were
mainly of predation and herbivory types, and removed the largest network
(\(S = 714\)) for computational efficiency reasons. Then, to this set we
added food webs from two different sources: the New Zealand dataset
(\(N = 21\); J. P. Pomeranz et al. 2018) and the Tuesday Lake dataset
(\(N = 2\); Cohen, Jonsson, and Carpenter 2003). Our complete dataset
thus contained a total of \(257\) food webs. All code and data to
reproduce this article are available at the Open Science Framework. Data
cleaning, simulations and analyses were conducted in Julia v1.6.1.

@@

We compared the performance of both heuristic MaxEnt models in
predicting these measures to the one of the null and neutral models (Box
2). We conducted these comparisons using two different datasets: (1) our
complete dataset including most food webs archived on Mangal, as well as
all food webs in the New Zealand and Tuesday Lake datasets, and (2) our
\emph{abundance dataset}, a subset of the complete dataset comprising
all food webs having data on their species' relative abundances
(\(N=19\)). Indeed, of the New Zealand and Tuesday Lake datasets, \(19\)
networks had data on species' relative abundances that were used in the
neutral model to better assess the performance of our heuristic models.
We compared our models' predictions using these two datasets separately
to minimize biases and to better represent food webs with abundance data
(tbl.~\ref{tbl:measures_all} and tbl.~\ref{tbl:measures_abund}).

Overall, we found that the models based on the joint degree sequence
(i.e.~the type II null and heuristic MaxEnt models) reproduced the
structure of empirical food webs much better than the ones based on
connectance (i.e.~the type I null and heuristic MaxEnt models). This
suggests that the predictive power of connectance might be more limited
than what was previously suggested (Poisot and Gravel 2014). On the
other hand, the neutral model of relative abundances was surprisingly
good at predicting the maximum trophic level and the network diameter.
However, with the exception of the network diameter, the type II
heuristic MaxEnt model was better at predicting network structure than
the neutral model for most measures considered. This might be because,
although neutral processes are important, they act in concert with niche
processes in determining species interactions Canard et al. (2014). The
joint degree sequence encodes information on both neutral and niche
processes because the number of prey and predators a species has is
determined by its relative abundance and biological traits. These
results thus show that having information on the number of prey and
predators for each species substantially improves the prediction of
food-web structure, both compared to models solely based on connectance
and to the ones solely based on species relative abundances.
